---
title: "TBD"
author: "Arjun Dhatt, Benjamin Draskovic, Yiqu Ding, Gantavya Gupta"
date: "10/16/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(rstanarm)
```

## Abstract

## Introduction

## Data

## Model

The model that we are using is multilinear regression. We want to estimate the preference towards the number of children of women across Canada(change this), using a sample obtained from the GSS data set. Due to the nature of GSS, the sample represents the population well enough to skip post-stratification. We use multilevel regression to predict the number of children a woman will have based on our variables of interest using `function` from `package.` 


## Results

```{r}
#load prepared data
my_data <- read.csv("gss-prepared-for-analysis .csv")
```

```{r}
#multilevel regression
#This does now work, need to look into a a binomial variable.
fit1 <- stan_glmer(
  total_children ~ (1 | age) + (1 | age_at_first_birth) + (1 | education) + (1 | income_family),
  family = binomial(link = "logit"),
  data = my_data
)
```

## Discussion

## References

- https://mc-stan.org/rstanarm/articles/mrp.html

- https://www.monicaalexander.com/posts/2019-08-07-mrp/

